Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-08 paper/main.tex
Started on Tahoe in general and added some references.

\usepackage{appendix} % Fixes formatting of appendicies
\usepackage{graphicx} % We *may* use images
\usepackage{hyperref} % Internal and external links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders

@@

\section{Tahoe-LAFS}

What is it, how/where are hash functions used, Python, pycryptopp

@@

\cite{nistround2}

@@

% BibTeX bibliography lives in external file
\bibliographystyle{plain}
\bibliography{ref_sha3}

>>>>

\usepackage{appendix} % Fixes formatting of appendices
\usepackage{graphicx} % We *may* use images
\usepackage{hyperref} % Internal and external links is nice
\hypersetup{pdfborder=0 0 0} % ..especially without red borders

@@

\section{Tahoe-LAFS}
%What is it, how/where are hash functions used, Python, pycryptopp
%comparison with RAID-6

The Tahoe Least-Authority Filesystem is a system for secure,
distributed data storage \cite{t_tahoe}. Tahoe was originally developed with
funding from the former web backup service provider Allmydata, but is now a
stand-alone Open Source project \cite{t_ars}.

New files saved using Tahoe follow this pattern:
\begin{enumerate}
\item The file is encrypted using AES.
\item The file is split up into \emph{N} parts using \emph{erasure coding}.
\item The parts are distributed to \emph{N} storage servers.
\end{enumerate}

The use of erasure coding enables Tahoe to recover a file using only a
predefined subset of the parts distributed to the storage servers.

% TODO: comparison with RAID?

\subsection{Advantages using a secure, distributed file system}
% Use cases?

@@

\cite{s_nistround2}

@@

% BibTeX bibliography lives in external file
\bibliographystyle{plain}
\bibliography{ref_sha3,ref_tahoe}
